Data Management for LSST Special Programs

### 2024-03-27 DMTN-065.tex
hotfix change record

\setDocAbstract{
Special Programs are additional survey areas and/or observing strategies that are driven by specific science 
goals which build on, or are beyond, the core science pillars of the Wide Fast Deep Main Survey.
In order to meet the requirements and enable science related to Special Programs, this document provides 
recommendations for Rubin Data Management regarding processing and serving data products for Special Programs.

\smallskip
Hardware and processing boundaries on the potential diversity of data from Special Programs
are discussed along with scenarios in which user-generated processing 
and data products might be needed to meet Special Programs' science goals.
}

\setDocChangeRecord{%
\addtohist{0}{2017-11-14}{Status: internal working document.}{Melissa Graham}
\addtohist{1}{2018-06-17}{Updated to finalize and issue.}{Melissa Graham}
\addtohist{2}{2021-12-01}{Updates per DM-20375.}{Melissa Graham}
\addtohist{3}{2023-10-19}{Updates per DM-32723.}{Melissa Graham}
}

>>>>

\setDocAbstract{
Special Programs are additional survey areas and/or observing strategies that are driven by specific science 
goals which build on, or are beyond, the core science pillars of the Wide Fast Deep Main Survey.
In order to meet the requirements and enable science related to Special Programs, this document provides 
recommendations for Rubin Data Management regarding processing and serving data products for Special Programs.
Hardware and processing boundaries on the potential diversity of data from Special Programs
are discussed along with scenarios in which user-generated processing 
and data products might be needed to meet Special Programs' science goals.
}

\setDocChangeRecord{%
\addtohist{0}{2017-11-14}{Status: internal working document.}{Melissa Graham}
\addtohist{1}{2018-06-17}{Updated to finalize and issue.}{Melissa Graham}
\addtohist{2}{2021-12-01}{Updates per DM-20375.}{Melissa Graham}
\addtohist{3}{2024-03-01}{Updates per DM-32723.}{Melissa Graham}
}

### 2024-03-27 ap_spcs.tex

Step 3. Special Processing with reconfigured pipelines. \\
First, a template image of appropriate depth for ``nightly" difference imaging is created.
At the end of each nightly sequence of observations, a pipeline based on recongfigured 
components of the LSST Science Pipelines is automatically triggered.
This pipeline creates nightly coadds in each filter and runs DIA using the template.
Alerts are \emph{not} produced, but unique and separate catalogs with the same format
as {\tt DiaObject} and {\tt DiaSource} are updated within 24 hours (not a requirement).
At the end of each season, deeply coadded images that include all of the DDF's visits 
from all years are re-generated, along with a separate {\tt Object}-like catalog.
All images and catalogs are stored in separate butler collections and TAP tables from
the Main Survey data products.

>>>>

Step 3. Special Processing with reconfigured pipelines. \\
First, a template image of appropriate depth for ``nightly" difference imaging is created.
At the end of each nightly sequence of observations, a pipeline based on recongfigured 
components of the LSST Science Pipelines could be automatically triggered.
This pipeline creates nightly coadds in each filter and runs DIA using the template.
Alerts are \emph{not} produced, but unique and separate catalogs with the same format
as {\tt DiaObject} and {\tt DiaSource} could be updated within 24 hours (not a requirement).
Instead of running daily, this processing might run weekly instead (TBD).
At the end of each season, deeply coadded images that include all of the DDF's visits 
from all years are re-generated, along with a separate {\tt Object}-like catalog.
All images and catalogs are stored in separate butler collections and TAP tables from
the Main Survey data products.

### 2024-03-27 sec_req.tex

\subsection{User Processing}\label{ssec:req_ug}

@@

>>>>

@@

This is a minor detail but, there are two different "10\%" values quoted here.
The accounting order is not in the requirements but Rubin Data Management considers
the 10\% for User-Generated Processing as coming off of the total capacity first,
with 90\% allocated for Rubin processing.
Then the 10\% for Rubin Special Processing comes from that 90\%,
and so is actually 9\% of the total capacity.
